---
title: "Analysis for project 3"
author: "Matias Janvin"
date: "12/4/2021"
output: html_document
---

# Survival analysis on the incidence of wildfires

```{r include=FALSE}
library(ggplot2)
library(tidyr)
library(dplyr)
library(corrplot)
library(maps)
library(survival)
library(timereg)
```


```{r include=FALSE}
# Read data
load("../Data/data_train_DF.RData")
data = data_train_DF
```


Having considered the subgroup of gridpoints that are highly susceptible to wildfires, we next  use survival analysis to study how temperature affects the incidence of wildfires. We will use Cox additive hazards regression to characterize how temperature affects the survival probability with respect to wildfire events, defined as the probability of not experiencing any wildfire event by month $t$ during a given year. To fix ideas, we first consider the survival during year 2015. The Kaplan-Meier estimator of the survival probability is given by

$$ \widehat{P}(T>t) = \prod_{T_i\leq t} \left( 1- \frac{\Delta N_{T_i}}{Z(T_i)} \right)~,$$

where $T_i$ is the time of the first wildfire in the geographical gridpoint $i$ during the year 2015, and $Z(T_i)$ is the number of gridpoints at risk of experience a first wildfire event just before time $T_i$.  We have plotted the Kaplan-Meier estimator for the year 2015 in Fig. \@ref(fig:survival) below. As can be seen in the plot, the first wildfire often occurs during March.



```{r survival, fig.cap="Kaplan-Meier estimator of the survival with respect to wildfire events during 2015",  echo=FALSE}
df.surv<- data.frame('ID'= paste(data$lon,data$lat) , 'start'=rep(0,nrow(data)) , 'stop'=data$month,  'count' =data$CNT, 'event'= as.numeric(data$CNT>=1)  , 'year'= data$year, 'Temp'=data$clim4-273 )
# Remove rows with missing values:
df.surv<- df.surv[
  !is.na(df.surv$ID)&
  !is.na(df.surv$start)&
  !is.na(df.surv$stop)&
  !is.na(df.surv$count)&
  !is.na(df.surv$event)&
  !is.na(df.surv$Temp)&
  !is.na(df.surv$year),
    ]
df.surv$start<-df.surv$stop
df.surv$stop<-df.surv$stop+1 # Increment month by 1 to consider incidence by the end of each month

#hist(table(df.surv$ID))


locations<-unique(paste(data$lon,data$lat))


# Next, we create a sample of this dataframe containing N=500 different gridpoints from year 2015.
N<- 1000 # Sample of 500 individuals
year<- 2013
set.seed(2)

df.sample<-df.surv[df.surv$year==year,]
df.sample<-df.sample[df.sample$ID %in% sample(unique(df.sample$ID) ,N),]
# table(table(df.sample$ID)) # Checking the number of measurements for each month



#Next, we remove entries for gridpoints after the first occurrence of a wildfire. 
fire.locations<-unique(df.sample$ID[df.sample$event==1])
#length(fire.locations)


df.truncated.sample <- df.sample[!df.sample$ID %in% fire.locations,]

for (i in fire.locations) {
  T.fire<-min(df.sample$stop[df.sample$ID==i & df.sample$event==1]) # Time of first occurence of fire in location i
  df.truncated.sample<-rbind(df.truncated.sample,df.sample[df.sample$ID==i & df.sample$stop <= T.fire ,])
}

# Kaplan-Meier estimator survival w.r.t. occurrence of at least 1 wildfire in 2015
fit.survival<-survfit(Surv(start,stop, event) ~ 1, data=df.truncated.sample,conf.type="plain")
plot(fit.survival,mark.time=TRUE, xlim=c(3,10), ylim=c(0,1), main="Survival with respect to wildfire in 2015", xlab='Month',ylab='Survival')

# Cox proportional hazards model fit for 2015
coxfit<-coxph( Surv(start,stop, event)  ~ Temp, df.truncated.sample)


```


Next, we fit a Cox proportional hazards regression model of the type

$$ \alpha(t\mid T_K; \beta) = \alpha_0(t)\exp\left(\beta \cdot T_C\right)$$
where $\alpha_0(t)$ is a baseline hazard, $T_C$ is the temperature (in degrees Celsius) and $\beta$ is regression coefficent for  $T_C$, which is to be estimated. Thus, the hazard ratio for an increase by 1 degree Celsius is given by
$$HR=\frac{\alpha(t\mid \theta; \beta)}{\alpha(t\mid \theta-1; \beta)}=\exp(\beta) ~.$$
For the year 2015, our Cox proportional hazards regression give the following results:

```{r echo=FALSE}
summary(coxfit)
```

Thus, temperature has a statistically significant effect on the hazard ratio for wildfire events. We have also repeated the analysis for other years and illustrated the resulting hazard ratio estimates with $95\%$ confidence intervals  in Fig. \@ref(fig:HR) below.


```{r HR, fig.cap="Evolution of hazard ratios over time", echo=FALSE}
j<-0
HR<-data.frame('HR'=0,'lower.95'=0,'upper95'=0,'year'=0) # Dataframe containing hazard ratios and confidence intervals for different years


for (y in unique(df.surv$year)) {
j<-j+1

df.sample<-df.surv[df.surv$year==y,]
df.sample<-df.sample[df.sample$ID %in% sample(unique(df.sample$ID) ,N),]

fire.locations<-unique(df.sample$ID[df.sample$event==1])
df.truncated.sample <- df.sample[!df.sample$ID %in% fire.locations,]

for (i in fire.locations) {
  T.fire<-min(df.sample$stop[df.sample$ID==i & df.sample$event==1]) # Time of first occurrence of fire in location i
  df.truncated.sample<-rbind(df.truncated.sample,df.sample[df.sample$ID==i & df.sample$stop <= T.fire ,])
}



coxfit<-coxph( Surv(start,stop, event)  ~ Temp, df.truncated.sample)
HR[j,c(1,2,3)]<-summary(coxfit)$conf.int[c(1,3,4)]
HR[j,4]<-y

}

# Plotting the confidence intervals over time
y.max<-max(HR$upper95)
y.min<-min(HR$lower.95)
plot(HR$year,HR$HR, 's', ylim=c(y.min,y.max), ylab='HR', xlab='Year', main='Evolution of hazard ratio for temperature over time')
lines(HR$year, HR$lower.95, 's', lty='dotted')
lines(HR$year,HR$upper95,'s',lty='dotted')
lines(HR$year,rep(1,length(HR$year)), col='red','s' ) 
```


Most years, the confidence intervals do not include the null value of the hazard ratio, shown as a red line on the above plot. This may suggest that temperature not only exacerbates wildfires in high risk geographical locations, but is also associated with new occurrences of wildfires in areas that where they do not usually occur. This may give an indication of the scale of evolution of wildfires in the future, if temperatures continue to rise.  
